Codebook

### 2020-01-13 raw_data/positive_results_in_registered_reports_codebook.Rmd
changed dataset file name and updated codebook accordingly

```{r prepare_codebook}
codebook_data <- import("positive_results_in_registered_reports_masterfile_data.xlsx")

# Read codebook from second sheet in Excel file.
dict <- import("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")

>>>>

```{r prepare_codebook}
codebook_data <- import("positive_results_in_registered_reports_data.xlsx")

# Read codebook from second sheet in Excel file.
dict <- import("positive_results_in_registered_reports_data.xlsx", sheet = "data_dictionary")
